%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Lachaise Assignment
% LaTeX Template
% Version 1.0 (26/6/2018)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Marion Lachaise & François Févotte
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{article}

\input{structure.tex} % Include the file specifying the document structure and custom commands

\usepackage{comment}
\usepackage{helvet}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{dsfont}
\usepackage{multirow}
\usepackage{color}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{bigints}
%\onehalfspacing
%\doublespacing
\usepackage{algorithm2e}
\usepackage{float}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{longtable}
\usepackage{enumerate}
\usepackage{mdframed}
\usepackage{framed}
\usepackage{url}
\usepackage[colorlinks,linkcolor=blue]{hyperref}
\usepackage{soul}

\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,      
    urlcolor=blue,
    citecolor=black,
}


\newcommand{\indep}{\mathrel{\text{\scalebox{1.07}{$\perp\mkern-10mu\perp$}}}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\bm}[1]{\mathbf{#1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\I}{\mathbb{I}}
\newcommand{\com}[1]{&&\mbox{(#1)}}
\newcommand{\note}[1]{\noindent{\color{red} [\textbf{Note:} #1]}}
\def\code#1{\texttt{#1}}

%----------------------------------------------------------------------------------------
%	ASSIGNMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{ECE 661: Homework \#1 \\ Linear Model, Back Propagation and Building a CNN}

\author{Yiran Chen}

\date{ECE Department, Duke University --- \today} 
%----------------------------------------------------------------------------------------

\begin{document}

\maketitle % Print the title

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\section*{Objectives} % Unnumbered section
Homework \#1 covers the contents of Lectures 02 $\sim$ 04. This assignment includes conceptual questions on the linear model, back propagation and convolutions, as well as lab questions involving trying out LMS algorithm and building and observing a CNN model.

The lab questions in this assignment don't involve the training of deep learning models.
So you are welcome to use your own computer to finish the labs.

Please refer to the {\color{blue} \textbf{NumPy/PyTorch tutorial}} slides on Sakai for the environment setup on your computer. 
If you intend to use the OIT server, please refer to the appendix on Page 7 of this assignment document for the environment setup.

\begin{warn}
\textbf{You are asked to complete the assignment independently.}

\vspace{6pt}
\noindent

This lab has a total of \textbf{100} points plus 10 bonus points, yet your final score cannot exceed 100 points. 
You must submit your report in PDF format and your original codes for the lab questions through \textbf{Sakai} before {\color{blue} \textbf{11:55:00pm, Thursday, September 15}}. 
You need to submit {\color{blue} \textbf{three individual files}} including (1) \textit{a self-contained report in PDF format} that provides answers to all the conceptual questions and clearly demonstrates all your lab results and observations, (2) \textit{a single code file} used to produce all the results for Lab: LMS algorithms; and (3) \textit{a Jupyter notebook file} for Lab: Simple NN. 
{\color{red}\textbf{Note that  20 percent of the grade will be deducted for the submissions uploaded in a zip file.}}

\end{warn}


\input{visualization.tex}
\clearpage
\input{Appendix.tex}





\end{document}
